\documentclass{article}

\usepackage[eandd]{neurips_2026}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{url}
\hypersetup{
  colorlinks=false,
  pdfborder={0 0 0},
}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{xspace}
\usepackage{placeins}
\usepackage{tabularx}

\newcommand{\sys}{MaxionBench\xspace}
\newcommand{\hotpotmaxionbench}{HOTPOTQA-MAXIONBENCH\xspace}
\newcommand{\ndcg}{nDCG@10}
\newcommand{\ecov}{evidence\_coverage@10}
\newcommand{\postinsertone}{post\_insert\_hit@10,1s}
\newcommand{\postinsertfive}{post\_insert\_hit@10,5s}
\newcommand{\maxrowp}{max-row p99\xspace}

\title{\sys: Conformance-Gated Decision Audits for Agentic Retrieval Memory}

\author{Anonymous Authors}

\begin{document}

\maketitle

\begin{abstract}
Agentic AI systems increasingly use retrieval stores as mutable operational memory:
agents insert evidence, query it under tail-latency budgets, and pay downstream
context costs for retrieved passages. Existing evaluations split these concerns
across static information-retrieval benchmarks and vector-database performance
tests, leaving operators without an auditable way to choose a retrieval stack under
deployment constraints. We present MaxionBench, a conformance-gated benchmark
that evaluates retrieval infrastructure as a deployment decision audit rather than
as a single leaderboard. A fixed adapter contract gates engines before scoring;
three workloads test static retrieval, post-insert retrievability, and multi-evidence
retrieval; and each decision card reports quality, a normalized context-cost proxy,
max-row p99 latency, budget stability, objective sensitivity, and paired margins.
In a single-node evaluation of FAISS CPU, LanceDB in-process,
pgvector, and Qdrant, a strict 200 ms max-row p99 policy selects FAISS CPU with
bge-small for all three workloads. Decision margins show that the static and
streaming workloads are cost-quality near-ties resolved by tail latency, while the
multi-evidence workload has both lower cost and higher evidence coverage than the
nearest strict-cost alternative. Changing the objective changes selected
configurations; matched audits show that an apparent aggregate pgvector quality
edge is indistinguishable from FAISS; and short screening runs fail to preserve
full-budget top-1 decisions on two workloads. MaxionBench therefore reports
objective-conditioned, auditable deployment evidence for retrieval-memory
selection.
\end{abstract}

\input{sections/01_introduction}
\input{sections/02_benchmark}
\input{sections/03_related_work}
\FloatBarrier
\input{sections/03_experiments}
\FloatBarrier
\input{sections/04_limitations}
\input{sections/05_conclusion}

\FloatBarrier
\clearpage
\bibliographystyle{plainnat}
\bibliography{references}

\clearpage
\appendix
\input{sections/appendix}

\input{checklist}

\end{document}
