\section{Related work}

Information-retrieval benchmarks provide the relevance backbone for this work. MS MARCO \citep{bajaj2016msmarco}, Natural Questions \citep{kwiatkowski2019natural}, KILT \citep{petroni2021kilt}, BEIR \citep{thakur2021beir}, SciFact \citep{wadden2020scifact}, FiQA \citep{maia2018fiqa}, and HotpotQA \citep{yang2018hotpotqa} supply reusable corpora, tasks, and judgments, but they do not specify retrieval-engine conformance, write/retrieve probes, context-cost estimates, or deployment decision rules. \sys reuses labeled retrieval evidence while adding the systems and decision-audit layer needed for local infrastructure choices.

Prior work on neural retrieval and RAG motivates the agent-facing evidence layer. Sentence-BERT \citep{reimers2019sentence}, DPR \citep{karpukhin2020dense}, ColBERT \citep{khattab2020colbert}, ANCE \citep{xiong2021approximate}, E5 \citep{wang2022text}, and MTEB \citep{muennighoff2023mteb} study representation quality and retrieval-model evaluation; REALM \citep{guu2020retrieval}, RAG \citep{lewis2020retrieval}, FiD \citep{izacard2021leveraging}, RETRO \citep{borgeaud2022improving}, RAGAS \citep{es2024ragas}, and RAGBench \citep{friel2024ragbench} study retrieval-conditioned generation or RAG evaluation. These papers clarify why retrieved evidence matters, while \sys asks a lower-level deployment question: can the retrieval infrastructure surface evidence under local p99, write, and context-budget constraints?

Vector-search systems and benchmarks usually emphasize algorithmic recall, throughput, indexing configuration, and operating mode. Product quantization \citep{jegou2011product}, FLANN \citep{muja2014scalable}, HNSW \citep{malkov2020efficient}, FAISS \citep{johnson2019faiss}, ANN-Benchmarks \citep{aumuller2020ann}, the NeurIPS billion-scale ANN challenge \citep{simhadri2021bigann}, and vector-database suites such as VectorDBBench \citep{vectordbbench} expose important search-performance surfaces. These benchmarks are complementary to \sys: they characterize ANN or product performance, whereas \sys fixes an agent-facing adapter contract and ties configured search behavior to retrieval quality, post-insert top-10 retrievability, context-token cost, and deployment objectives.

Benchmark methodology and agent-memory work motivate the reporting style. MLPerf Inference \citep{reddi2019mlperf} emphasizes rules and reproducible system comparisons; HELM \citep{liang2023helm} emphasizes multi-metric transparency; datasheets \citep{gebru2021datasheets} and Croissant metadata \citep{mlcommons2024croissant} motivate explicit dataset documentation; and tail-latency work motivates high-percentile latency reporting \citep{dean2013tail}. AgentBench \citep{liu2023agentbench}, MemGPT \citep{packer2023memgpt}, LongMemEval \citep{wu2024longmemeval}, and LoCoMo \citep{maharana2024locomo} evaluate agent behavior or long-term memory. \sys applies the reporting discipline to retrieval stores used as local agent memory.
