\section{Experimental boundaries and broader impact}

\sys reports a fixed, reproducible CPU-only evaluation setting for retrieval-memory decisions. The experiments cover FAISS CPU, LanceDB in-process, pgvector, and Qdrant under the adapter settings recorded in the supplementary material; distributed retrieval, GPU indexing, cloud variability, second-machine portability, and multi-tenant workloads are natural extensions of the same conformance-gated protocol. The S3 multi-evidence workload uses \hotpotmaxionbench{}, a frozen paragraph-level HotpotQA preprocessing, and the S2 streaming workload measures top-k retrievability after inserts. Engine-level quality differences are configured-search differences under the MaxionBench adapter settings. The S3 multi-evidence paired audit uses FAISS exact FlatIP as the bge-base reference, and future service-engine sweeps can vary higher probe and ef settings within the same adapter contract.

The uncertainty estimates describe the recorded benchmark runs. Confidence intervals are query- or event-level summaries, and \maxrowp latency is reported with the hardware/runtime profile that produced it. S1 single-hop and S2 streaming change top-1 recommendations between B0 and B2, while S3 multi-evidence keeps the same top-1 recommendation but has low full-rank correlation; these budget effects are part of the experimental result. The broader impact is methodological: a reproducible benchmark can help operators choose lower-cost, lower-latency retrieval infrastructure while keeping quality, post-insert retrievability, objective choice, budget level, and paired margins visible.
